---
title: "HW 6"
author: "JAYNA CLARK"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

Import data set

```{r}
load("house_prices.rda")
```

(a) Use facet_wrap to draw line plots to represent the trend for 
house_price_index over years for each state. .
Please have three ticks on the x axis which are for years 1980, 2000, and 2020.
Since you have limited space your
labels can be ’80, ’00, and ’20 for these ticks.

```{r}
ggplot(house_prices, aes(x = date, y = house_price_index)) +
  geom_line() +
 facet_wrap(~ state)+
  scale_x_continuous(
      breaks = as.Date(c("1980-01-01", "2000-01-01", "2020-01-01")),
    labels = c("’80", "’00", "’20")) +
  labs(
    x = "Year",
    y = "House Price Index",
    title = "Trends in House Price Index by State") +
  theme_minimal()
```

(b) Use gather() function from tidyr to reshape your data in a way that it will
have measure and value columns for house_price_index and unemploy_perc, 
respectively, in two columns. You should leave out remaining attributes 
by using ”-” in front them inside the function. Then, direct the output 
to a new data frame called house_reshaped Please refer to examples we did 
in class.

```{r}
house_reshaped <- house_prices |>
  gather(key = "measure", value = "value", house_price_index, unemploy_perc)
```

(c) Use house_reshaped to replicate the graph in 2a with two lines where 
each represents house_price_index and unemploy_perc over the years for each
state. Once you have the chart, please comment on it as to whether it’s a
good graph to present those two pieces of information.

```{r}
ggplot(house_reshaped, aes(x = date, y = value, color = measure))+
  geom_line() +
  facet_wrap(~state) +
  scale_x_continuous(
    breaks = as.Date(c("1980-01-01", "2000-01-01", "2020-01-01")),
    labels = c("’80", "’00", "’20")) +
  labs(title = "Trends in House Price Index and Unemployment % by State",
       x = "Year",
       y = "Value",
       color = "Measure") +
  theme_minimal() 

```
It is a good graph to present House price index- unemployment percent is not 
shown well as it is much smaller and it is a percentage. It is not shown well 
because the y-axis goes up to 300 whereas the unemployment % has a maximum value
of about 18. 

